---
title: "Interactive Plots"
author: "Pengfei Lou"
date: "`r Sys.Date()`"
output: html_document
---

```{r,echo=TRUE,warning=FALSE,message=FALSE}
pacman::p_load(
  plotly,
  esquiess,
  ggplot2,
  DT,
  dplyr,
  tigris,
  sf,
  leaflet,
  htmltools,
  knitr
)
```

```{r,include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,        # Hides code from all chunks
  message = FALSE,     # Hides messages from all chunks
  warning = FALSE      # Hides warnings from all chunks
  
)
```

```{r,results='hide'}
dat<-read.csv("D:\\project-Geo\\final_combined.csv")

str(dat)
dat$County<-as.factor(dat$County)
dat$Category<-as.factor(dat$Category)
dat$Variable<-as.factor(dat$Variable)

dat<-dat %>% filter(dat$R.2>0.85) 
dat<-dat %>% filter(!County %in% c("Cherokee","Henry","Paulding"))
```


## Figure 1.Exploratory Data Analysis: Feature Distribution

```{r,echo=TRUE,message=FALSE, warning=FALSE}
# Create ggplot with side-by-side boxplots and jittered points positioned to the side of the boxplot
# Each jitter point is color-coded by the 'Variable' column
dat$Variable_jitter <- as.numeric(factor(dat$Variable)) + 0.35  # Slightly shifts jittered points for better visibility

p <- ggplot(dat, aes(x = County, y = Obesity.Risk, fill = Category)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.5, width = 0.4, position = position_nudge(x = -0.7)) +  
  # Creates boxplots with adjusted width, transparency, and nudged slightly to the left
  
  geom_jitter(aes(x = Variable_jitter, text = paste("Variable(%):", Variable,
                                                    "<br>Prevalence(%):", round(Value, 2), 
                                                    "<br>Obesity Risk(%): ", round(Obesity.Risk, 2),  
                                                    "<br>Category:", Category)), 
              width = 0.1, size = 2, alpha = 0.9) +  
  # Adds jittered points with a small horizontal spread, positioned slightly to the right
  
  scale_x_discrete(labels = levels(factor(dat$County))) +  
  # Ensures correct labeling of the 'County' variable on the x-axis
  
  labs(title = "Exploratory Data Analysis: Feature Distribution",
       x = "County",
       y = "Obesity Risk(%)",
       fill = "Category") +  
  # Adds labels and title for better readability
  
  theme_minimal()  
  # Applies a clean, minimalistic theme for better visualization

# Convert ggplot object to an interactive Plotly plot
# Ensures a tooltip with relevant information appears when hovering over a data point
ggplotly(p, tooltip = "text")  



```

**Key Takeaways**

- Identifies the distribution of key predictor variables related to obesity risk across counties.
- Highlights how different factors (e.g., sleep, income) contribute to variations in obesity prevalence.
- Compares environmental, behavioral, and sociodemographic categories to detect key trends and patterns.



```{r,results='hide'}
ga_counties<-counties(state="GA",cb=TRUE,resolution="20m")
ga_counties <- ga_counties %>% rename(County=NAME)
selected_counties <- ga_counties %>% filter(County %in% dat$County) %>%
  left_join(dat,by="County")
#unique(ga_counties)
```

## Figure 2.Region Bias

```{r,echo=TRUE}

# Filter for "Insufficient Sleep Prevalence" variable
selected_counties <- selected_counties %>%
  filter(Variable == "Insufficient Sleep Prevalence")

# Define color palette based on R² values
pal <- colorNumeric(palette = "YlOrRd", domain = selected_counties$R.2, na.color = "transparent")

# Create hover text with multiple variables
selected_counties$hover_text <- paste0(
  "<strong>County:</strong> ", selected_counties$County, "<br>",
  "<strong>Obesity Risk(%):</strong> ", round(selected_counties$Obesity.Risk, 3), "<br>",
  "<strong>Insufficient Sleep Prevalence(%):</strong> ", selected_counties$Value, "<br>"
)

# Create a title for the map
title <- tags$div(
  tags$h3("Region Bias",
          style = "text-align:center; font-weight:bold; background:white; padding:3px;"))

# Generate the interactive leaflet map
leaflet(selected_counties) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~pal(R.2),  # Fill color varies by R²
    fillOpacity = 0.7,      
    color = ~pal(R.2),  # Border color also varies by R²
    weight = 2,  # Border thickness
    label = lapply(selected_counties$hover_text, HTML),  # Display hover tooltip
    highlight = highlightOptions(weight = 3, color = "blue", bringToFront = TRUE)
  ) %>%
  addLegend(pal = pal, values = selected_counties$R.2, title = "R² Value", position = "bottomright") %>%
  addControl(title, position = "topright") %>%  # Change "topcenter" to "topright"
  # Add county name labels at the center of each county
  addLabelOnlyMarkers(
    data = selected_counties,
    lng = st_coordinates(st_centroid(selected_counties))[,1],  # Get X (longitude)
    lat = st_coordinates(st_centroid(selected_counties))[,2],  # Get Y (latitude)
    label = ~County,  # Display county name
    labelOptions = labelOptions(noHide = TRUE, textOnly = TRUE, style = list("color" = "black", "font-weight" = "bold"))
  )


```

**Key Takeaways**

- Identifies counties where the model performs best and worst based on R² values, with darker shades indicating better model fit.
- Highlights regional variations in obesity risk, revealing spatial patterns across different counties.
- Illustrates the relationship between insufficient sleep prevalence and obesity risk, helping to understand how sleep behavior influences health outcomes.

